plots with prolactin

### 2019-12-06 analysis/16_PRL.Rmd
new illustrations, new prolactin stuff

p4 <- ggplot(meanPRL, aes(treatment, m)) +
   geom_errorbar(aes(ymin=m-se, ymax=m+se, color = treatment), width=.1) +
   geom_image(aes(image = iconpath), size = 0.06)  +
   geom_image(aes(image = music , y = m + 0.5), size = 0.04) +
   labs(x = "parental care stages", y = "Pituitary PRL") +
   mytheme() +
   ylim(c(16,22)) +
   theme(axis.text.x = element_text(angle = 45)) +
  theme(legend.position = "none") +
  scale_color_manual(values = colorscharmaip2) +
  geom_hline(yintercept=16.8) +
  geom_hline(yintercept=17.8) +
  geom_hline(yintercept=18.8) +
  geom_hline(yintercept=19.8) +
  geom_hline(yintercept=20.8) 
p4

```

>>>>

p4 <- ggplot(meanPRL, aes(treatment, m)) +
   geom_errorbar(aes(ymin=m-se, ymax=m+se, color = treatment), width=.1) +
   geom_image(aes(image = iconpath), size = 0.06)  +
   geom_image(aes(image = music , y = m + 0.5), size = 0.04) +
   labs(x = "parental care stages", y = "Pituitary PRL") +
   mytheme() +
   ylim(c(16,22)) +
   theme(axis.text.x = element_text(angle = 45)) +
  theme(legend.position = "none") +
  scale_color_manual(values = colorscharmaip2) +
  geom_hline(yintercept=16.8) +
  geom_hline(yintercept=17.8) +
  geom_hline(yintercept=18.8) +
  geom_hline(yintercept=19.8) +
  geom_hline(yintercept=20.8) 
p4
```

```{r geneshormones}
candidates.pit$bird_id <- candidates.pit$bird

geneshormones <- left_join(candidates.pit, hormones) %>%
  select(-X1, -V1, -okay, - icons, -music, -iconpath) %>%
  drop_na()
head(geneshormones)

ggplot(geneshormones, aes(x = plasma_conc, y = PRL)) +
  geom_point(aes(color = treatment)) +
  facet_wrap(~hormone, scales = "free_x") +
    geom_smooth(method = "lm", color = "grey")

prolactin2 <- read_csv("../results/07_prolactin2.csv")
head(prolactin2)
geneshormones2 <- left_join(candidates.pit, prolactin2) %>%
  drop_na()
head(geneshormones)

ggplot(geneshormones2, aes(x = plasma_conc, y = PRL)) +
  geom_point(aes( color = treatment)) +
  geom_smooth(method = "lm", color = "grey") +
  facet_wrap(~hormone, scales = "free") 
```

```{r}
write.csv(candidates.pit, "../results/16_pitPRL.csv")
```
